---
title: "Illustration"
author: "19024"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to SC19024}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

__SC19024__ is a simple R package developed to achieve several common tasks in statistics computation. The first function RMonte provides an easy way to do Monte Carlo Integration. It can automatically reduce the variance by several methods. The second function can improve the efficiency of bootstrap in estimating mean value of a dataset by implementing all the process in Cpp. It can provide variance and different kind of confidence interval as well.

#RMonte

Argument:

FUN: the integrated function

low,up: integration interval

N: number of simulation

layer: number of stratification

Method: way to reduce the variance

```{r}
library(SC19024)
RMonte(FUN=exp,low = 0,up = 5,N=1000,layer = 5, Method = 'control')
RMonte(FUN = function(x){x^2},0,1,1000,5,'control')

```

An addtional function TestVariance is available to test the variance reduced by this package.

For example
```{r}
# normal monte carlo integration in interval [0,5]
TestVariance(RMonte,100,exp,0,5,1000,1,'None')

# reduce by antithetic variable
TestVariance(RMonte,100,exp,0,5,1000,1,'Antithetic')

# reduce by control variable
TestVariance(RMonte,100,exp,0,5,1000,1,'control')

#reduce by stratification
TestVariance(RMonte,100,exp,0,5,1000,3,'None')

# stratification and control variable
TestVariance(RMonte,100,exp,0,5,1000,3,'control')

```

Another example

```{r}
TestVariance(RMonte,100,function(x){x^2},0,5,1000,1,'None')
TestVariance(RMonte,100,function(x){x^2},0,5,1000,1,'control')

```

the variance are reduced more than 1000 times.

#CBoot

Argument:

DATA: a vector contain all the data

sims: number of replicates

Method: the type of confidence interval

alpha: the confidence parameter

An example:
```{r}
Cboot(DATA = 1:100,sims = 100,Method = 'Perc',alpha = 0.05)
```

Comparing with the package boot:

```{r}
library(boot)
library(microbenchmark)
microbenchmark(Cboot(DATA = 1:100,sims = 10,Method = 'Perc',alpha = 0.05),boot(1:100,statistic = function(data,index){mean(data[index])},R=10))
```
